An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-04-10 mixedwindow.tex
Rewrite introduction to theory section
This commit rewords parts of the introduction to the theory section,
and hopefully makes it work better as a stand alone subsection.

This section presents the new \oos\ statistic.
Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
(Theorem~\ref{res:1} lists the assumptions formally).  In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If the linear model is
correctly specified, so $\varepsilon_{t+1}$ is an \mds\ with respect to
$\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots)$,%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We also present results that allow
  $\varepsilon_{t+1}$ to be serially correlated.} %
then we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistic on the RHS of
Equation~\eqref{eq:5}, where $R$ is the size of the training sample and $P$
the size of the test sample used to evaluate the forecasting models.
\citet{ClW:06} use a second forecast $\hat{y}_{t+1}$ as $v_t$.  They
use a rolling window of length $R$ (making $\hat{y}_{t+1}$ a
function of $y_t, x_{t-1}, z_{t-1} \dots, y_{t-R+1}, x_{t-R}$ and
$z_{t-R}$ where $z_t$ is another weakly dependent random process),
which is kept finite as $T \to \infty$, so $\hat{y}_{t+1}$ inherits
the weak dependence properties of the variables used to estimate it.
Keeping $R$ finite ensures that the conditional variance remains
positive, so the sum obeys a \clt.  This method of ensuring normality
was introduced by \citet{GiW:06}.  In \citet{ClW:06}, the coefficients $\btrue$ are
assumed to be zero so $\varepsilon_{t+1}$ is observed directly (under
the null hypothesis) and Clark and West propose using this statistic
to test the null that $\varepsilon_{t+1}$ is an \mds\ with respect to
$\mathcal{F}_t$.  In \citet{ClW:07}, $\btrue$ is unknown but is
estimated with a fixed-length rolling window as well, so
\begin{equation*}
  \tilde{\beta}_t = \Big(\sum_{s=t-R+1}^t x_{s-1} x_{s-1}'\Big)^{-1}
  \sum_{s=t-R+1}^t x_{s-1} y_s
\end{equation*}
and $\hat{\varepsilon}_{t+1} = y_{t+1} - x_t'\tilde{\beta}_t$ replaces
$\varepsilon_{t+1}$ in \oos\ test statistic.  Unfortunately,
$\hat{\varepsilon}_{t+1}$ is not an \mds\ even when
$\varepsilon_{t+1}$ is, so the statistic is no longer asymptotically
mean-zero normal, even though this approximation performs well in the
simulations reported by \citet{ClW:07}.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\btrue$ and produce
$\hat{\varepsilon}_{t+1}$; i.e.
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06}, these conditions are ensured if $v_t$ is another
forecast of $y_{t+1}$ based on a fixed length rolling window.

Section~\ref{sec:1a} lays out the necessary assumptions for our
results and Section~\ref{sec:1b} presents the details.

>>>>

This section presents the new \oos\ statistic; first we give an
informal motivation of the statistc, then section~\ref{sec:1a}
presents the paper's key assumptions and section~\ref{sec:1b} presents
our formal theoretical results.

Suppose for now that a researcher is interested in
predicting the target variable $y_{t+1}$ with a vector of regressors
$x_t$; also let $v_t$ be another random process that may contain information about
$y_{t+1}$ and suppose that
$(y_t, x_t, v_t)$ is stationary and weakly dependent
In addition,
let $\btrue = (\E x_t x_t')^{-1} \E x_t y_{t+1}$ be the pseudotrue
coefficient of the regression of $y_{t+1}$ on $x_t$ and define
$\varepsilon_{t+1} = y_{t+1} - x_t'\btrue$.  If this linear model is
correctly specified, then $\varepsilon_{t+1}$ is an \mds\ with respect
to the information set
\begin{equation*}
\mathcal{F}_t \equiv \sigma((x_t, v_t, y_t), (x_{t-1}, v_{t-1},
y_{t-1}),\dots),
\end{equation*}
and we can see immediately that
\begin{equation}
  \label{eq:4}
  \oclt{t} \varepsilon_{t+1} (v_t - x_t'\btrue)
\end{equation}
obeys an \mds\ \clt%
\footnote{This claim assumes that the asymptotic variance of the
  sample average is uniformly positive, a requirement that we will
  address in Section~\ref{sec:1b}.} %
and is asymptotically normal as $P \to \infty$, with $R$ an
arbitrary starting value%
\footnote{It will be clear momentarily why the
  summation begins at $R+1$ instead of $1$.} %
and $P = T - R$.%
\footnote{Section~\ref{sec:1b} discusses conditions under which the
  \mds\ condition holds. We will also present results that allow
  $\varepsilon_{t+1}$ to be serially correlated.} %
Straightforward algebra \citep{ClW:07} shows that
\begin{equation}
  \label{eq:5}
  \tfrac{1}{\sqrt{P}} \osum{t} \varepsilon_{t+1} (v_t -
  x_t'\btrue) = \tfrac{1}{2 \sqrt{P}} \osum{t} \Big[(y_{t+1} -
  x_t\btrue)^2 - (y_{t+1} - v_t)^2 + (x_t'\btrue - v_t)^2 \Big].
\end{equation}

\citet{ClW:06,ClW:07} base their \oos\ statistics on the RHS of
Equation~\eqref{eq:5}, but using a second forecast of $y_{t+1}$ as
$v_t$. (Call it $\hat{y}_{t+1}$.) They use a rolling window of length
$R$ to estimate $\hat{y}_{t+1}$;%
\footnote{Making $\hat{y}_{t+1}$ a function of $y_t, x_{t-1}, z_{t-1}
\dots, y_{t-R+1}, x_{t-R}$ and $z_{t-R}$, where $z_t$ is another weakly
dependent random process} %
$R$ is kept finite as $T \to \infty$, so
$\hat{y}_{t+1}$ inherits the weak dependence properties of the
variables used to estimate it. Using a finite window length $R$ avoids
the degeneracy that often arises in OOS test statistics (see
\citealp{ClM:01}, and \citealp{Mcc:07}), so the conditional variance
of the OOS average remains positive and the average obeys a \clt, an
approach introduced by \citet{GiW:06}.

\citet{ClW:06,ClW:07} develop a test of whether $\varepsilon_{t+1}$ is
an \mds. In the 2006 paper, Clark and West assume that the
coefficients $\btrue$ are zero under the null, making
$\varepsilon_{t+1}$ observed directly. This restriction is relaxed in
the 2007 paper where $\btrue$ is unknown and estimated with length-$R$
rolling window. Now the estimated linear model's prediction errors,
$\hat{\varepsilon}_{t+1}$, replace $\varepsilon_{t+1}$ in the \oos\
test statistic. Unfortunately, $\hat{\varepsilon}_{t+1}$ is not an
\mds\ even when $\varepsilon_{t+1}$ is, so the statistic is no longer
asymptotically mean-zero normal, even though this approximation
performs well in simulations.

This paper proposes using the same basic \oos\ statistic, 
but using a recursive window to estimate $\btrue$ and produce
$\hat{\varepsilon}_{t+1}$; so
\begin{equation}
  \label{eq:8}
  \hat{\beta}_t = \Big(\sum_{s=2}^{t} x_{t-1} x_{t-1}'\Big)^{-1}
  \sum_{s=2}^t x_{t-1} y_t.
\end{equation}
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\hat{\beta}_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\hat{\beta}_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under the null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

This overview has presented an especially simple version of the result
to make the intuition as clear as possible. The next section lists the
specific assumptions that need to hold.
